Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2024-04-04 latex/figure2.tex
Update IDE figures

\begin{minipage}[b]{0.50\linewidth}

{\centering

\includegraphics{src/ide/ide1.pdf}

}

\end{minipage}%
%
\begin{minipage}[b]{0.50\linewidth}

{\centering

\includegraphics{src/ide/ide2.pdf}

}

\end{minipage}%

\caption{\label{fig-ide}Screenshots of Visual Studio Code showing
tooltips and highlighted type errors. \texttt{Constant} are assigned
with \texttt{assign(...,\ constant=True)} and can be used to link
\texttt{Variable}s initial conditions, while trying to use a
\texttt{Parameter} instead is flagged as type errors (red underlining).
The IDE automatically recognizes \texttt{e} as an \texttt{Equation}, and
provides autocompletion of the variables. A tooltip is shown when
composing models, which show the expected variables and their default
values. The IDE highlights wrong names (\texttt{z} is not a name in
\texttt{Model}) and mismatched types (\texttt{x} is \texttt{Variable}
and \texttt{a} must be a number or a \texttt{Constant})}

>>>>

\begin{minipage}[b]{0.50\linewidth}
{
    \centering 
    \includegraphics{src/ide/ide1.pdf}
}
\end{minipage}%
%
\begin{minipage}[b]{0.50\linewidth}
{
    \centering
    \includegraphics{src/ide/ide2.pdf}
}
\end{minipage}%

\caption{
    \label{fig-ide}
    Screenshots of Visual Studio Code showing
    tooltips (green arrows) and
    highlighted type errors (red arrows).
    On the left,
    we show that \texttt{a},
    a \texttt{Constant} assigned with \texttt{assign(...,\ constant=True)},
    can be used for \texttt{Variable b}'s initial condition.
    Instead,
    it is flagged as a type error (red underlining)
    when using \texttt{c}, a \texttt{Parameter},
    for \texttt{Variable d}'s initial condition,
    The IDE automatically recognizes \texttt{e} as an \texttt{Equation},
    and provides autocompletion of the \texttt{Model}'s components.
    A tooltip is shown when composing models (green arrow, right),
    which show the expected variables and their default values.
    The IDE highlights wrong names (\texttt{z} is not a name in \texttt{Model})
    and mismatched types (\texttt{x} is \texttt{Variable} and \texttt{a} must be a number or a \texttt{Constant})
}
